\chapter{Conclusion and Future Work\label{chap6}}
\section{Conclusion}
In this project, we work as a team to design and implement a multifunctional intelligent rover using Webots simulation. The designed rover succeeds in finishing all assigned tasks. However, our team does not stop here. We go a little bit further by including what might happen in the real world in our design. We consider the external environment, such as angle of the sun, the dusk on the road, and the internal physical property of the rover, like the centre of mass during development, ensuring that our design is robust even in real-world scenarios. These results come from a joint effort of our team members. We also attribute our success to the proper use of project management skills.
\section{Future Work\label{future_work}}
Although we have tried our best to make our design close to reality, our design still some limitations since Webots is, as a matter of fact, not real and we do not explore it to the full extent. Due to time restriction, we only choose solutions from a limited amount of image processing or chassis control algorithms. The following points are possible extensions in the future:
\begin{enumerate}
    \item Improve the path finding and object detection by taking advantage of cutting-edge image processing methods
    \item Make a more detailed comparison among solutions of different sensors and choose a optimal one
    \item Improve the chassis control algorithm by receiving more signals from the visual system
\end{enumerate}